Kindly Bent to Free Us

### 2018-05-24 kindly/main.tex
Inference.
More inference.
Add kind scheme and type validity.

\documentclass[sigconf,author]{acmart}\settopmatter{printfolios=true}

@@

\begin{figure*}[h]
  \centering
  \input{syntax}
  \caption{Syntax}

  \input{kinds}
  \caption{Kind rules -- $\haskind{P}{\E}{\tau}{k}$ }

  \input{typing}
  \caption{Typing rules -- $\hastype{P}{\E}{e}{\tau}$ }

  \input{semantics}
  \caption{Reduction rules -- $\ered{I}{E}{e}{v}$ }

\end{figure*}

>>>>

\documentclass[manuscript,author]{acmart}\settopmatter{printfolios=true}

@@

\begin{figure*}[h]
  \centering
  \input{syntax}
  \caption{Syntax}
\end{figure*}
\begin{figure*}[h]
  \input{kinds}
  \caption{Constraint rules -- $\entail{C}{k}$ }
\end{figure*}
\begin{figure*}[h]
  \input{types}
  \caption{Type validity rules -- $\tyval{C}{\E}{\tau}$ }
  \input{inference}
  \caption{Inference rules -- $\inferW{\Sigma}{(C,\psi)}{\bf{\E}}{\bf{e}}{\tau}$ }
\end{figure*}
% \begin{figure*}[h]
%   \input{semantics}
%   \caption{Reduction rules -- $\ered{I}{E}{e}{v}$ }

% \end{figure*}

\section*{Todo}

\begin{itemize}
\item Add type constructors
\item Properly ensure that it respects HM(X) (cylindric, \dots)
\item Show principal type inference:
  \begin{itemize}
  \item Principal constraint system
  \item Regular constraint system: $\Ceq{\tau}{\tau'} \implies \fv{\tau} = \fv{\tau'}$.
  \item Solved forms are in simplified form.
    $C\in S, \entail{C}{\Ceq{\tau}{\tau'}} \implies \entail{}{\Ceq{\tau}{\tau'}}$.
  \end{itemize}
\item Show equivalence with the logic-based system.

\end{itemize}

\begin{lemma}
  Without loss of generality, we can consider that
  kind inequalities in satisfiable constraints
  are only done on kind variables.

  \begin{proof}
    Consider the constraint $\Cleq{k}{k'}\Cand C$.
    \begin{itemize}
    \item If $k$ and $k'$ are both constants, it can be removed.
    \item If the constraint is $\Cleq{\kvar}{\kaff}$ or $\Cleq{\kun}{\kvar}$, it can be removed.
    \item If the constraint is $\Cleq{\kvar}{\kun}$ or $\Cleq{\kaff}{\kvar}$, we
      can substitute $\kvar$ by its value in $C$.
    \end{itemize}
  \end{proof}
\end{lemma}
